Compositional equivalences based on Open pNets

### 2020-03-12 2016-Weak-FH-Bisim/WeakBisim.tex
check: comments Eric

\TODO{Check, nouvelle formulation, Eric}
Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists. The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$. $[a]$ denotes a list with a single element.

\ERIC{Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists. The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}. $[a]$ denotes a sequence with a single element.}

As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
Thus we define $\vis{\set\beta}$\footnote{\ERIC{La notation
    $\vis{\beta}$ n'est pas tres parlante, mais je n'ai pas vraiment
    de meilleure idee...}} as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]

\ERIC{As required actions are now sequences of observable actions, we need an operator to build them from set of (single) hole actions that occur in open transitions.
Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]}

\ERIC{As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$. Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.}

>>>>

\TODO{Check, nouvelle formulation, Eric}
\LUDO{checked, slight changes}
Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences. The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}. $[a]$ denotes a sequence with a single element.

As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e. an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]

As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$. Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
